### 2020-02-28 README.Rmd
added plot title

```{r}
library(zonebuilder)
library(tmap)
london_zones = zb_zone(london_area, london_cent)
zb_plot(london_zones)
```

@@

The lower-level fuinctionm

The functions `zb_doughnuts` generates rings:

```{r}
tmap_border = tm_shape(london_area) + tm_borders()
tmap_arrange(
  qtm(zb_doughnut(london_area, london_cent, n_circles = 5), title = "Doughnuts") + tmap_border,
  qtm(zb_segment(london_cent, n_segments = 20), title = "Segments") + tmap_border
)
```

```{r}
tmap_arrange(
  qtm(zb_zone(london_area, london_cent, n_segments = 1, n_circles = 5), title = "Doughnuts") + tmap_border,
  qtm(zb_zone(london_area, london_cent, n_segments = 12, n_circles = 1, segment_center = TRUE), title = "Segments") + tmap_border,
  qtm(zb_quadrat(london_area, london_cent, ncol = 4), title = "Quadrants") + tmap_border
)
```

>>>>

```{r}
london_zones = zb_zone(london_cent, london_area)
zb_plot(london_zones)
```

@@

The function `zb_zone` makes use of `zb_doughnut` and `zb_segment`, which can also be used directly:

```{r}
par(mfrow=c(1,2))
zb_plot(zb_doughnut(london_cent, london_area, n_circles = 5), title = "Doughnuts")
zb_plot(zb_segment(london_cent, n_segments = 20), title = "Segments")
zb_plot(zb_zone(london_cent, n_circles = 4, n_segments = 4), title = "Zone with 4 circles and 4 segments")
```

<!-- tmap_arrange( -->
<!--   zb_view(zb_doughnut(london_cent, london_area, n_circles = 5), title = "Doughnuts"), -->
<!--   zb_view(zb_segment(london_cent, n_segments = 20), title = "Segments") -->
<!--  ) -->
